pseudobulk_CMP

### 2021-09-14 pseudobulk_vs_bulk/pseudobulk_allPops.Rmd
start automating pseudobulk analysis

## Load libraries
```{r setup}
library(dplyr)
library(Seurat)
library(ggplot2)
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/pseudobulk_vs_bulk/")
```

>>>>

```{r setup}
knitr::opts_knit$set(root.dir = "~/Desktop/10XGenomicsData/msAggr_scRNASeq/pseudobulk_vs_bulk/")
```

## Load libraries
```{r}
library(dplyr)
library(Seurat)
library(ggplot2)
```
